---
title: "Lei_Zhuo_STAT425_HW23"
author: "Zhuo Feng Lei (zlei5)"
date: "3/25/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
```

## Question 1 
```{r}
#Part A
data = read.csv("facebook_teach.csv")
control = data[data$Trt==0,]
treatment = data[data$Trt==1,]
t.test(treatment$post_lrn,control$post_lrn,var.equal = T)
```
The difference in the sample mean score is 7.15009. The two-sided p value for the t-test is 0.01564.
```{r}
#Part B
fit1b = lm(post_lrn~pre_lrn+Trt,data = data)
summary(fit1b)
```
Conditioning on pre_lrn, facebook intervention will increase the post_lrn by 6.8385 units. The p-value of the corresponding test of significance of the regression coefficient is .0193. Since the p-value is less than .05 (our alpha), we know that treatment is a significant variable in predicting post learning achievement scores.

```{r}
#Part C
fit1c = lm(post_lrn~pre_lrn+Trt+pre_lrn*Trt,data = data)
summary(fit1c)
```
The p-value of pre_lrn:Trt is .0818. Since its greater than .05, we fail to reject the hypothesis of addictivity. There is no evidence of an interaction between treatment and the pre-treatment  achievement score in predicting post-treatment achievement scores.

## Question 2

```{r}
data(shoes)

results = c()
assignments = matrix(0,1024,10)
for (i in 1:1024){
  assignments[i,] = as.numeric(intToBits(i))[1:10]
}
assignments = (assignments*2)-1

for(i in 1:1024)
  {
  results[i] = t.test((shoes$A - shoes$B)*assignments[i,])$statistic
  }

t.observed = t.test(shoes$A - shoes$B)$statistic
approx.pval = mean(abs(results) >= abs(t.observed))
approx.pval
```

