---
title: "Lei_Zhuo_STAT425_HW15"
author: "Zhuo Feng Lei (zlei5)"
date: "2/22/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(alr4)
library(lmtest)
```

## Question 1 
```{r}
data(jevons)
fit1 = lm(Age~Weight,data = jevons)
summary(fit1)
confint(fit1,level = .95)
```

## Question 2 
```{r}
#Part A/B
fit2 = lm(Age~Weight,weights = n ,data = jevons)
summary(fit2)
confint(fit2,level = .95)
```
```{r}
#Part C
w_2 = diag(fit2$weights)
w_2
solve(w_2)
```

## Question 3 
```{r}
#Part A/B
fit3 = lm(Age~Weight,weights = n/SD^2,data = jevons)
summary(fit3)
confint(fit3)
```
```{r}
#Part C
w_3 = diag(fit3$weights)
w_3
solve(w_3)
```

## Question 4 
```{r}
#Part A
data = read.csv("lpga2009.csv")
fit4a = lm(prize~percentile,data = data)
bptest(fit4a)
```

There is evidence to reject the null hypothesis of constant error variance.

```{r}
#Part B
fit4b = lm(log(prize)~percentile,data = data)
bptest(fit4b)
```
There is evidence to reject the null hypothesis of constant error variance.

## Question 5 
The linear model does not satisfy the Gauss-Markov conditions because $var(\epsilon)\neq\sigma^2 I$ since $\sum$ is a symmetric and positive invertible matrix. We need $\sum$ to be an identity matrix so we have to transform the model by C. 

First, we multiply both sides by C:

$$Cy = CX\beta+C\epsilon$$

$z = Cy, M = CX, \delta = C\epsilon$:

$$z = M\beta+\delta$$

where $E(\delta)=0$ and 

$$var(\delta)=Cvar(\epsilon)C^T = \sigma^2CC^{-1}C^{-T}C^T = \sigma^2I$$

Thus, the Gauss-Markov conditions are met after transformation.
