---
title: "Lei_Zhuo_STAT425_HW22"
author: "Zhuo Feng Lei (zlei5)"
date: "3/13/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mfp)
library(glmnet)
```

## Question 0 
```{r}
data(bodyfat)
bodyfat = bodyfat[,-(3:4)]
smp_size = floor(0.5 * nrow(bodyfat))
set.seed(425)
train_ind = sample(seq_len(nrow(bodyfat)), size = smp_size)
train = bodyfat[train_ind, ]
test = bodyfat[-train_ind, ]
```

## Question 1 
```{r}
#Ridge Regression
xtrain = as.matrix(train[,-2])
ytrain = as.matrix(train[,2])
xtest = as.matrix(test[,-2])
ytest = as.matrix(test[,2])
ridge_mod = glmnet(xtrain,ytrain,alpha=0)
ridge_cv_out = cv.glmnet(xtrain, ytrain, alpha=0)
best_lambda_ridge = ridge_cv_out$lambda.min
best_lambda_ridge
```

```{r}
#lasso 
lasso_mod = glmnet(xtrain,ytrain,alpha=1)
lasso_cv_out = cv.glmnet(xtrain,ytrain,alpha=1)
best_lambda_lasso = lasso_cv_out$lambda.min
best_lambda_lasso
```

We fit the model using our training data. Then, we use cross-validation to determine the appropriate lambda. We select the lambda with the lowest value because it gives the best penalization. The shrinkage penalty for lasso is $\lambda \sum|\beta_j|$ and the shrinkage penalty for ridge regression is $\lambda \sum|\beta_{j}^2|$.

## Question 2
```{r}
#ridge MSE
ridge_pred = predict(ridge_mod, s=best_lambda_ridge, newx = xtest)
MSE_ridge = mean((ytest-ridge_pred)^2)
MSE_ridge
```

```{r}
#lasso MSE
lasso_pred = predict(lasso_mod, s=best_lambda_lasso, newx = xtest)
MSE_lasso = mean((ytest-lasso_pred)^2)
MSE_lasso
```

## Question 3
```{r}
lasso_coef = predict(lasso_mod, type = 'coefficients', s = best_lambda_lasso)[1:15,]
lasso_coef[lasso_coef != 0]
```
```{r}
fit =lm(brozek~age+neck+abdomen+hip+ankle+biceps+forearm+wrist,data=test)
summary(fit)
```


The lasso model has the lowest MSE when compared with the ridge regression model. The lasso model model with lambda chosen by cross-validation contains only 8 variables. These 8 variables are shown above. The model is significant based on F test p value and individual t test’s p values. It explains 72.21% of variance in the response. Therefore, it should work decently in predicting bodyfat percentage.