---
title: "Lei_Zhuo_STAT425_HW18"
author: "Zhuo Feng Lei (zlei5)"
date: "3/1/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
```

## Question 1
```{r}
data = read.csv("fishermen_mercury.csv")
fit1 = lm(TotHg~fisherman+height+weight,data=data)
summary(fit1)
```
```{r}
par(mfrow=c(2,2))
plot(fit1)
```
In the residuals vs fitted plot, there seems to be a slight downward trend, thus the data is not linearized. In addition, the points are not evenly spread so constant variance is violated.

In the normal qqplot, some of the points doesn't fall on the straight line, hence normality is not satisfied.

In the scale-location plot, there is an upward trend. This tells us that constant variance is violated.

In the residuals vs leverage plot, there are no points behind the cook's distance contour lines. Hence, according to cook's distance, there are no apparent influential points. 

## Question 2
```{r}
trans_fit1 = lm(TotHg^(2/5)~fisherman+height+weight,data=data)
boxcox(trans_fit1)
```
Based on the box-cox plot, there is evidence that the transformation is appropriate since the lambda value is very close to 1 and 1 falls within the interval.

```{r}
par(mfrow=c(2,2))
plot(trans_fit1)
```
Residuals vs fitted plot shows a roughly flat trend so linearity seems to be satisfied. The points aren't very evenly spread so constant variance is violated.

In the normal qq plot, the points on both ends doesn't fall on the straight line so normality is not satisfied.

In the scale-location plot, there is a roughly upward trend which indicates that constant variance is violated. 

In the residuals vs leverage plot, none of the points are highly influential according to cook's distance.
## Question 3 
```{r}
data2 = read.csv("napa_marathon_fm2015.csv")
fit2 = lm(Hours~Age,data = data2)
par(mfrow=c(2,2))
plot(fit2)
```
In the residuals vs fitted plot, there seems to be a slight parabolic trend. This indicates that the data is not very linearized. However, the points are spread equally so constant variance does not seem to be violated.

In the normal qq plot, the points on both ends fall away from the line. This tells us that normality is not very satistified.

In the scale-location plot, the trend appears to be roughly flat. This indicates that constant variance is not violated.

In the residuals vs leverage plot, we do not see the cook's distance contour lines. According to cook's distance, there doesn't seem to be any highly influential points.

## Question 4
```{r}
trans_fit2 = lm(sqrt(Hours)~Age,data = data2)
boxcox(trans_fit2)
```
Based on the box-cox plot, there is evidence that the transformation is appropriate since the lambda value is very close to 1 and 1 is within the lambda interval.

## Question 5

$$\lim_{\lambda\to0}\frac{\frac{d}{d\lambda}(y^\lambda-1)}{\frac{d}{d\lambda}\lambda} = \lim_{\lambda\to0}\frac{y^\lambda ln(y)}{1}$$

$$ = \frac{y^0*ln(y)}{1} = ln(y)$$

$$\lim_{\lambda\to0}\frac{y^\lambda-1}{\lambda}\to ln(y)$$