---
title: "STAT 425 HW 1"
author: "Zhuo Feng Lei (zlei5)"
date: "1/20/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Question 1

Fitted Values:

$\hat{y_i}=\hat{\beta_0}+\hat{\beta_1}x_i$

Sum of Residuals:

$\sum\hat{u}_i^2=\sum(y_i-\hat{y_i})^2$

$\sum\hat{u}_i^2=\sum(y_i-\hat{\beta_0}+\hat{\beta_1}x_i)^2$

$\delta{SSR}/\delta{\hat{\beta_0}}=\sum2(y_i-\hat{\beta_0}+\hat{\beta_1}x_i)*(-1)=0$

$\delta{SSR}/\delta{\hat{\beta_0}}=\sum(y_i-\hat{\beta_0}+\hat{\beta_1}x_i)$

$y_i-\hat{y}=\hat{u}_i$

$\sum{\hat{u}}_i=0$

$\hat{\bar{u}}_i=0$

$\delta{SSR}/\delta{\hat{\beta_1}}=\sum2(y_i-\hat{\beta_0}+\hat{\beta_1}x_i)*(-x_i)=0$

$\sum(\hat{u_i}*x_i)=0$

$\sum(y_i-\hat{\beta}_0-\hat{\beta_{1}xi})=0$

$\sum{y_i}-n\hat{\beta_0}-\hat{\beta}_1\sum{x_i}=0$

$n\bar{y}-n\hat{\beta_0}-\hat{\beta}_1n\bar{x}=0$

$\hat{\beta_0}=\bar{y}-\hat{\beta}_1\bar{x}$

$\sum(x_iy_i)(y_i-\bar{y})=\sum{x_i}(y_i-\bar{y})$

$\sum(x_iy_i-n\bar{x}\bar{y})=\hat{\beta}_1(\sum{x_i^2}-n\bar{x}^2)$

$\bar{\beta}=\sum{x_iy_i}-n\bar{x}\bar{y}/(\sum{x_i}^2-n\hat{x}^2)$

## Question 2
```{r}
winner.url = "http://www.stat.ufl.edu/~winner/data/"
tmp.url = paste0(winner.url, "cruise_ship.dat")
st = c(1,21,41,49,57,65,73,81,89)
en = c(20,40,48,56,64,72,80,88,97)
wds = diff(c(st, en[length(en)]))
cship = read.fwf(tmp.url, widths = wds, strip.white = T)
colnames(cship)=c("ShipName","CruiseLine","Age","Tonnage","passengers", "Length","Cabins","pdensity","crew")
```

```{r}
b1 = (sum(cship$crew*cship$passengers)-(nrow(cship)*mean(cship$passengers)*mean(cship$crew)))/(sum(cship$passengers^2)-nrow(cship)*mean(cship$passengers)^2)
b0 = mean(cship$crew)- (b1*mean(cship$passengers))

b1
b0
```

```{r}
lm(crew~passengers,data = cship)
```
Intercept is 1.6783 and the slope is .3314. 

## Question 3
If there are 0 passengers, each cruise ship will contain 167.83 crew members. For every 100 passengers, the number of crew members on the cruise ship will increase by 33.14. (I scaled the coefficients by 100 since the units will given in 100s.)

## Question 4 
$\sum(y_i-\hat{\beta}-\hat{\beta}x_i)(1+x_i)=0$

$\sum{y_i+y_ix_i}-\hat{\beta}\sum{1+x_i}-\hat{\beta}\sum{x_i+x_i^2}=0$

$\sum{y_i+y_ix_i}=\hat{\beta}(\sum(1+x_i)+\sum(x_i+x_i^2))$

$\hat{\beta}=\sum{y_i+y_ix_i}/(\sum(1+x_i)+\sum(x_i+x_i^2))$

## Question 5 
```{r}
x=c(1,3,2,5,1)
y=c(3,5,1,7,2)
b = sum(y+y*x)/(sum(1+x)+sum(x+x^2))
b
```

