---
title: "Lei_Zhuo_STAT425_HW19"
author: "Zhuo Feng Lei (zlei5)"
date: "3/4/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(alr4)
```

## Question 1

```{r}
#Part A
data(lakemary)
fit = lm(Length~Age+I(Age^2),data = lakemary)
summary(fit)
```
```{r}
#Part B
plot(lakemary$Age,lakemary$Length)
x.grid <- seq(min(lakemary$Age), max(lakemary$Age), len=100)
lines(x.grid, predict(fit, data.frame(Age=x.grid)), lty=3)
```
```{r}
#Part C
par(mfrow=c(2,2))
plot(fit)
```
The points in the residuals vs fitted plot shows a roughly flat trend so linearity is satisfied. 

Constant variance is not violated since the trend in scale-location plot is roughly flat.

The normal qq plot shows points in a a relative straight line so normality is decently satisified.

According to cook's distance, there are no highly influential points in the residuals vs leverage plot.

## Question 2
```{r}
#Part A
fitgen = lm(Length~factor(Age),data = lakemary)
fitlof = anova(fit,fitgen)
fitlof
```

Sum of squares for pure error is 8812.7 and sum of squares for lack-of-fit is 108.01.

Part B: Since the p-value is greater than our alpha (.05), we failed to find evidence to reject the quadratic model.

## Question 3
```{r}
hybrid = read.csv("hybrid_reg.csv")
fit1=lm(msrp~mpgmpge+accelrate,data=hybrid)
summary(fit1)
par(mfrow=c(2,2))
plot(fit1)
```

In the residuals vs fitted plot, there is a parabolic trend. This indicates that linearity is not satisfied. 

In the normal qqplot, the points on one end deviate from the straight line. Normality is partially satisfied.

In the scale-location plot, the trend is roughly flat. Therefore,constant variance is not violated.

According to cook's distance, there is no highly influential points in the residuals vs leverage plot.
```{r}
fit2=lm(msrp~mpgmpge*accelrate,data=hybrid)
summary(fit2)
par(mfrow=c(2,2))
plot(fit2)
```

In the residuals vs fitted plot, there is a parabolic trend. This means that linearity is not satifised.

In the normal qq plot, some points don't fall on the straight line. Normality is partially satisfied.

In the scale-location plot, the trendline is roughly flat. Therefore, constant variance is not violated.

According to cook's distance, there are no highly influential points in the residuals vs leverage plot.

Neither of the models seem to be very appropriate for the hybrid's data.
## Question 4
```{r}
fit3=lm(msrp~mpgmpge*poly(accelrate,2,raw=T),data=hybrid)
summary(fit3)
```

```{r}
par(mfrow=c(2,2))
plot(fit3)
```
In the residuals vs fitted plot, the trend is roughly flat thus linearity is satisfied.

In the normal qq plot, most of the points fall on the straigh line so most of the data satisfies normality.

In the scale-location plot, the trend is roughly flat so constant variance is not violated.

According to cook's distance, there are no highly influential points since no points resides past the contour lines in the residuals vs leverage plot. 
## Question 5
```{r}
anova(fit1,fit2)
```
Null Hypothesis is that model 1 suffices in predicting msrp. Alternative hypothesis is that model 2 fits better.

The degrees of freedom is 1. 

The p-value is 3.85e-06 which is less than .05. Thus, we reject the null hypothesis. There is evidence that model 2 fits better than model 1 when predicting msrp.


```{r}
anova(fit2,fit3)
```
Null Hypothesis is that model 2 suffices in predicting msrp. Alternative hypothesis is that model 3 fits better.

The degrees of freedom is 2. 

The p-value is 0.005064 which is less than .05. Thus, we reject the null hypothesis. There is evidence that model 3 fits better when predicting msrp.

We should use model 3 to predict msrp. When compared, model 2 fits better than model 1. However, model 3 fits better than model 2. Thus model 3 is best model to predict msrp out of the 3 models.

