---
title: "Lei_Zhuo_STAT428_HW32"
author: "Zhuo Feng Lei (zlei5)"
date: "4/28/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1a
```{r}
library(faraway)
data(aflatoxin)
```

```{r}
fit1 = glm(cbind(total-tumor,tumor)~dose,family = binomial(link = "logit"),data = aflatoxin)
summary(fit1)
fit1_trans = glm(cbind(total-tumor,tumor)~log(dose+1),family = binomial(link = "logit"),data = aflatoxin)
summary(fit1_trans)
```
```{r}
fit2 = glm(cbind(total-tumor,tumor)~dose,family = binomial(link = "probit"),data = aflatoxin)
summary(fit2)
fit2_trans = glm(cbind(total-tumor,tumor)~log(dose+1),family = binomial(link = "probit"),data = aflatoxin)
summary(fit2_trans)
```

```{r}
fit3 = glm(cbind(total-tumor,tumor)~dose,data=aflatoxin,family="binomial"(link="cloglog"))
summary(fit3)
fit3_trans = glm(cbind(total-tumor,tumor)~log(dose+1),data=aflatoxin,family="binomial"(link="cloglog"))
summary(fit3_trans)
```
The log(dose+1) is not an appropriate transformation. Models with the transformation have higher AIC and residual deviance values when compared to the models without the transformation.

## Question 1b

The untransformed model with the probit link has the lowest residual deviance value out of all the models. Therefore, that is my best model.

## Question 1c
```{r}
coef(fit1)
x = 3.03603648/0.09008878
x
```
$$.5 = \frac{1}{1+e^{-X^TB}}$$
$$ e^{-X^TB}=1$$
$$-X^TB=log(1)$$
$$X = -B_0/B $$

## Question 1d
```{r}
#transformed model with probit link is our best model
newdata = data.frame(dose=c(25))
predict(fit2,newdata,se.fit = T)
```
```{r}
0.4378986-(1.96*0.1682523)
0.4378986+(1.96*0.1682523)
```

