---
title: "Lei_Zhuo_STAT425_HW25"
author: "Zhuo Feng Lei (zlei5)"
date: "3/29/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(faraway)
```

## Question 1
```{r}
data(pvc)
```

```{r}
#operator
tapply(pvc$psize,pvc$operator,mean)
tapply(pvc$psize,pvc$operator,sd)
```

```{r}
#resin
tapply(pvc$psize,pvc$resin,mean)
tapply(pvc$psize,pvc$resin,sd)
```

## Question 2 
```{r}
#no interaction
no_int_model = lm(psize~factor(resin)+factor(operator),data = pvc)
summary(no_int_model)
#with interaction
int_model = lm(psize~factor(resin)*factor(operator),data = pvc)
summary(int_model)
```

## Question 3
```{r}
anova(int_model)
```
Since the p-value is .7599, greater than alpha (0.05), interaction is not significant in predicting psize. Therefore, we should use the no interaction model to predict psize. 

## Question 4
```{r}
par(mfrow=c(2,2))
plot(no_int_model)
```
There is a slight positive trend in the residuals vs fitted plot, thus linearity and constance varaince is violated.
Only some of the points on the normal q-q plot follows a straight line. Normality is not sastified.
The trend in the scale-location plot shows a slighly downward trend. Thus constant variance is violated.
According to the constant leverage plot, points 37,45, and 47 may be outliers. Further testing is needed to verify. 

```{r}
critval = qt(0.05/(2*nobs(no_int_model)), df=df.residual(no_int_model)-1, lower=FALSE)
which(abs(rstudent(no_int_model)) > critval)
```
Based on studentized residuals and Bonferroni-adjusted critical value, point 45 is an outlier. 

## Question 5
```{r}
t = TukeyHSD(aov(psize~factor(resin)+factor(operator),data=pvc))
t
```

```{r}
which(t$`factor(resin)`[,4]<=.05)
```
```{r}
which(t$`factor(operator)`[,4]<=.05)
```

Resin 3-1,4-1,5-1,6-1,7-1,3-2,4-2,5-2,6-2,7-3,8-3,7-4,8-4,8-5,7-6,8-6,8-7 are significant because their p-values are less than alpha and their CI does not contain 0.

Operators 3-1,3-2 are significant because their p-values are less than alpha and their CI does not contain 0. 