---
title: "Lei_Zhuo_STAT425_HW16"
author: "Zhuo Feng Lei (zlei5)"
date: "2/25/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(alr4)
```

## Question 1 
```{r}
#Part A
data(lakemary)
fit1 = lm(Length~Age,data = lakemary)
summary(fit1)
```

```{r}
#Part B
plot(lakemary$Age,lakemary$Length)
abline(fit1)
```

```{r}
#Part C
plot(fit1, which = 1)
```
Based on the residuals vs fitted plot, a linear model does not seem to fit the data as there seems to be a quadratic trend.

## Question 2 
It is possible to perform a lack-of-fit test for this data even though the error variance is unknown because there are independent replications at each of the x values.

## Question 3 
```{r}
fitgen1 = lm(Length~factor(Age),data = lakemary)
fit1lof = anova(fit1,fitgen1)
fit1lof
```

Part A: Sum of Squares for pure errors is 8812.7 and 3080.2 for lack of fit. 

Part B: $\tilde{\sigma}^2 = \frac{8812.7}{72} = 122.398611111$

Part C: Since the p-value is less than .05 (our alpha), we found evidence to reject the linear model. 

## Question 4 
```{r}
#Part A
data = read.csv("napa_marathon_fm2015.csv")
fit4 = lm(Hours~Age,data = data)
plot(fit4, which = 1)
```
Based on the residuals vs fitted diagnostic plot, the linear model does not seem to fit the data as there seems to be a quadratic trend.

```{r}
#Part B
fitgen4 = lm(Hours~factor(Age),data = data)
fit4lof = anova(fit4,fitgen4)
fit4lof
```
```{r}
fit4lof$`Sum of Sq`[2]
```
```{r}

```

Since the p-value is less than .05(our alpha), we reject the null hypothesis. We found evidence to reject the linear model. 

## Question 5
```{r}
fit5 = lm(Hours~poly(Age,2,raw = T),data = data)
fit5lof = anova(fit5,fitgen4)
fit5lof
```

Since the p-value is greater than .05, we do not find evidence that the quadratic model does not fit the data.