---
title: "Lei_Zhuo_STAT428_HW31"
author: "Zhuo Feng Lei (zlei5)"
date: "4/24/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(faraway)
```

## Question 0
```{r}
data(pima)
pima[,2:8][pima[,2:8]==0]<-NA
summary(pima)
```

## Question 1
```{r}
pima = na.omit(pima)
fit = glm(test~pregnant+glucose+diastolic+triceps+insulin+bmi+diabetes+age,family = binomial,data=pima)
summary(fit)
```
The variables that were significant at alpha=.05 is glucose,bmi, and diabetes since their respective p-values are lower than alpha.

## Question 2
```{r}
fit2 = step(fit,direction = "backward",trace = F)
summary(fit2)
```

## Question 3

For every one unit increase in pregnant, the log odds of test=1 vs test = 0 increases by 0.083953.
For every one unit increase in glucose, the log odds of test=1 vs test = 0 increases by 0.036458.
For every one unit increase in bmi, the log odds of test=1 vs test = 0 increases by 0.078139.
For every one unit increase in diabetes, the log odds of test=1 vs test = 0 increases by 1.150913.
For every one unit increase in age, the log odds of test=1 vs test = 0 increases by 0.034360.

## Question 4
```{r}
table(predicted = fitted(fit2) > 0.5, actual = pima$test)
```
```{r}
(232+75)/nrow(pima)
```
78.32% of the data were correctly predicted.

## Question 5
```{r}
#those who truly did
75/(75+55)
```
57.69% of those who truly did were predicted correctly.
```{r}
#those who didn't
232/(232+30)
```
88.55% of those who truly didn't have diabetes were predicted correctly.
