---
title: "Lei_Zhuo_STAT425_HW24"
author: "Zhuo Feng Lei (zlei5)"
date: "3/28/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1 
```{r}
data = read.table("bacterial-soap.txt",col.names = c("BacterialCounts","Method"))
data
```

```{r}
#Part A
tapply(data$BacterialCounts, data$Method, mean)
tapply(data$BacterialCounts, data$Method, sd)
```

```{r}
#Part B
model = lm(BacterialCounts~factor(Method),data = data)
anova(model)
```
P-value is .001111. Since the p-value is less than alpha, we reject the null hypothesis. There is evidence to conclude that the mean bacterial counts for all methods is not equal.

```{r}
#Part C
par(mfrow=c(2,2))
plot(model)
```
The residuls vs fitted plot shows a roughly flat trend so constant variance is satisfied. Linearity is also satisfied.
Most points on the normal q-q plot follows a straight line. Normality is decently satisfied.
The scale-location plot is roughly flat so constant variance is satisfied.
Points 27,26,7 may be possible outliers according to the constant leverage plot. 
```{r}
#Part D
critval = qt(0.05/(2*nobs(model)), df=df.residual(model)-1, lower=FALSE)
which(abs(rstudent(model)) > critval)
```
There are no outliers since none exceeded the Bonferroni critical value.

```{r}
#Part E
TukeyHSD(aov(BacterialCounts~factor(Method),data=data))
```
The pairs that are significantly different is AntibacterialSoap-AlcoholSpray, Soap-AlcoholSpray, and Water-AlcoholSpray. We know these 3 pairs are significant because their confidence intervals do not contain 0 and their p-values are lower than .05. 




