---
title: "Lei_Zhuo_STAT425_HW10"
author: "Zhuo Feng Lei (zlei5)"
date: "2/11/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1 
```{r}
data = read.csv("hybrid_reg.csv")
fit = lm(msrp~mpgmpge+accelrate,data = data)
leverage = hat(model.matrix(fit))
which.max(leverage)
data[151,]
```
Observation 151 (C-Max Energi Plug-in with msrp=32950, accelrate = 11.76 and mpgmpge=100) has the highest leverage. 

```{r}
data[which.max(fit$residuals),]
```
The Cadillac Escalade has the highest studentized residual with msrp=78932.81, accelrate=9.09, and mpgmpge = 22.35.

```{r}
st_res = rstudent(fit)
data[which.max(st_res),]
```

The Cadillac Escalade has the highest studentized residual with msrp=78932.81, accelrate=9.09, and mpgmpge = 22.35.

## Question 2 
```{r}
plot(st_res,fit$residuals)
```
The graph is not in a straight line because the studentized residuals depends on $\sqrt{1-h_{ii}}$. In order for it to be in a straight line, the denominator needs to be a constant. Since the points have different leverage, th estudentized residuals will be different from the least squares residuals.

## Question 3 
We know that $H = X(X^TX)^{-1}X^T$. Using the cyclic property of trace, we get $tr((X^TX)^{-1}X^TX)$. Because $(X^TX)^{-1}$ is inverse of $X^TX$, we get $tr(I_{pxp})$ where I is the identity matrix. $tr(I_{pxp}) = Rank X = p'$

## Question 4 
$var(\epsilon)=E(\epsilon^2)-E(\epsilon)^2$ We know that $E(\epsilon)^2=0$ thus we have $var(\epsilon)=E(\epsilon^2)-0$. We know from lecture that $var(\epsilon) = \sigma^2(I-H)$. Thus, $E(\epsilon^2)=\sigma^2(I-H)$.

## Question 5
Estimator is unbiased if $E(\hat{\sigma^2})=\sigma^2$. 

$$E(\hat{\sigma^2})=\frac{E(SSE)}{n-p'}$$

$$ = \frac{\sum{E(\hat{\epsilon^2})}}{n-p'}$$

$$ = \frac{\sum{\sigma^2(1-h_{ii})}}{n-p'}$$

$$ = \frac{\sum{\sigma^2}-\sigma^2\sum{h_{ii}}}{n-p'}$$

$$ = \frac{n\sigma^2-\sigma^2\sum{h_{ii}}}{n-p'}$$

$$ = \frac{\sigma^2(n-\sum{h_{ii}})}{n-p'} = \frac{\sigma^2(n-tr(H))}{n-p'}$$

$$ = \frac{\sigma^2(n-p')}{n-p'} = \sigma^2$$. Thus, it is an unbiased estimator.