---
title: "Lei_Zhuo_STAT425_HW26"
author: "Zhuo Feng Lei (zlei5)"
date: "4/1/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
```{r}
data = read.csv("golf_driver (1).csv")
data
```
```{r}
#Part A

#Driver
tapply(data$totdist,data$club, mean)
#Golfer
tapply(data$totdist,data$golfer, mean)
```

```{r}
#Part B
model = lm(totdist~factor(club)+factor(golfer),data = data)
anova(model)
```

The p-value for the F test studying driver effects is 0.01589. Since the p-value is less than alpha (.05), we reject the null hypothesis. There is evidence that drivers is significant in predicting total distance. 

```{r}
#Part C
TukeyHSD(aov(totdist~factor(club)+factor(golfer),data = data))
```
The pairs of drivers that are significantly different are 4-2 and 4-3. Their p-value is less than alpha (.05) and their confidence intervals does not contain 0.

The pairs of golfers that are significantly different are 3-1,4-1,6-1,3-2,4-2,6-2,4-3,5-3,6-3,6-4, and 6-5 for the same reasons as mentioned previously.

```{r}
#Part D
anova(lm(totdist~factor(club),data = data))
par(mfrow=c(2,2))
plot(lm(totdist~factor(club),data = data))
```

Without the block, the p-value for the f-test studying the driver's effects is .8729. The p-value is greater than alpha, so we fail to reject the null hypothesis. Without the block, we conclude that driver is not significant in predicting total distance. 

When not blocking  on golfer, the assumptions we violate is linearity (downward trend in residuals vs fitted plot), normality (many points on the normal q-q plot does not fall in a straight line), and constance variance (downward trend in residuals vs fitted plot and scale-location plot).

```{r}
#Part e
TukeyHSD(aov(totdist~factor(club),data = data))
```
Unlike the results in part c, the results in part e shows that none of the driver pairs are signficantly different. All of the p-values are greater than alpha (.05) and all of the confidence intervals contain 0. 
