---
title: "STAT 425 HW 1"
author: "Zhuo Feng Lei (zlei5)"
date: "1/16/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

```{r}
winner.url = "http://www.stat.ufl.edu/~winner/data/"
tmp.url = paste0(winner.url, "cruise_ship.dat")
st = c(1,21,41,49,57,65,73,81,89)
en = c(20,40,48,56,64,72,80,88,97)
wds = diff(c(st, en[length(en)]))
cship = read.fwf(tmp.url, widths = wds, strip.white = T)
colnames(cship)=c("ShipName","CruiseLine","Age","Tonnage","passengers", "Length","Cabins","pdensity","crew")
```

## Question 1 
```{r}
summary(cship$passengers)
summary(cship$crew)
```

  On average, there is 1846 passengers on a cruise ship. The least amount of passengers on a cruise ship is 66. The largest number of passengers on a cruiseship is 5400.
  On average, there is 779.4 crew members on a cruise ship. The least amount of crew members on a cruise ship is 59 crew members. The largest number of crew members on a cruiseship is 2100. 

## Question 2
```{r}
ggplot(cship) + geom_point(aes(passengers,crew)) + xlab("Number of Passengers on a Cruise Ship (100s)") + ylab("Number of Crew Members on a Cruise Ship (100s)")
```
As the numbers of passengers on a cruise ship increase, the number of crew members on the cruise ship also increases.

## Question 3
```{r}
correlation = cor(cship$passengers,cship$crew)
```
The correlation between passengers and crew members on a cruiseship is `r correlation`. 

## Question 4
$y_i=\beta_0+\beta_1 x_i+\beta_2x_i^2+e_i$ 

## Question 5 
$y_i=\beta_1+2\beta_2x_i$
